Illustration of Adaptive Shrinkage

### 2016-10-03 analysis/adaptive_shrinkage.Rmd
In adaptive_shrinkage.Rmd, I found it confusing that the same colour scheme was used in plot_pvalues as above, but this plot shows `log(s)`, whereas above the plots show `1/s`. It seems that it would be better to reverse the colour scheme for the `pval_plot` to better correspond to the above plots.

**Note:** I find it confusing that you are using the same colour scheme here as
above, but you are showing `log(s)`, whereas above you are showing `1/s`. It
seems that it would be better to reverse the colour scheme for the `pval_plot`
to better correspond to the above plots. –Peter

```{r plot_pvalues}
pval_plot = function (df)
  ggplot(df,aes(x = pnorm(-abs(betahat/s)),y = lfsr,color = log(s))) +
  geom_point() + facet_grid(.~scenario) + xlim(c(0,0.025)) +
  xlab("p value") + ylab("lfsr") +
  scale_colour_gradient2(midpoint = 0,low = "blue",
                         mid = "white",high = "red")

>>>>

```{r plot_pvalues}
pval_plot = function (df)
  ggplot(df,aes(x = pnorm(-abs(betahat/s)),y = lfsr,color = log(s))) +
  geom_point() + facet_grid(.~scenario) + xlim(c(0,0.025)) +
  xlab("p value") + ylab("lfsr") +
  scale_colour_gradient2(midpoint = 0,low = "red",
                         mid = "white",high = "blue")
